Reformulating phylogenetic mixed models to improve flexibility and speed

### 2020-02-20 phyloglmm_ms.tex
caption and x-label tweaks
submitted, need to chat about merging with lme4/glmmTMB

%\include{abstract}

@@

\begin{center}
\begin{figure}[H]
  \includegraphics[scale=0.7]{./figure/msplot.pdf}
  \caption{Comparison of multi-group model parameter estimates. The horizontal line shows the true value of the parameters in the simulation model. Models capable of fitting all parameters (\pkg{lme4} and \pkg{glmmTMB}) fit well for all parameters. \pkg{pez} and \pkg{phyr} estimates for n = 100 and 500 are missing because the models did not converge within 30 minutes.
  }
  \label{msplot}
\end{figure}
\end{center}
\begin{center}
\begin{figure}[H]
  \includegraphics[scale=0.7]{./figure/mstime.pdf}
  \caption{Comparison of multi-group model computational speed.}
  \label{msplot_time}
\end{figure}
\end{center}
\begin{center}
\begin{figure}[H]
  \includegraphics[scale=0.7]{./figure/mscoverage.pdf}
  \caption{Comparison of multi-group model coverage.}
  \label{msplot_coverage}
\end{figure}
\end{center}

@@

>>>>

\include{abstract}

@@

\begin{center}
\begin{figure}[H]
  \includegraphics[scale=0.7]{./figure/msplot.pdf}
  \caption{Comparison of multi-group model parameter estimates. The horizontal line shows the true value of the parameters in the simulation model. Models capable of fitting all parameters (\pkg{lme4} and \pkg{glmmTMB}) fit well for all parameters. \pkg{pez} and \pkg{phyr} estimates for n = 100 and 500 are missing because the models did not converge within 30 minutes.
  }
  \label{msplot}
\end{figure}
\end{center}
\begin{center}
\begin{figure}[H]
  \includegraphics[scale=0.7]{./figure/mstime.pdf}
  \caption{Comparison of multi-group model computational speed.}
  \label{msplot_time}
\end{figure}
\end{center}
\begin{center}
\begin{figure}[H]
  \includegraphics[scale=0.7]{./figure/mscoverage.pdf}
  \caption{Comparison of multi-group model coverage. The black line shows the nominal coverage, and the blue ribbon the 95\% binomial confidence interval based on 100 simulated fits.}
  \label{msplot_coverage}
\end{figure}
\end{center}

@@

\section*{Achnowledgements}

We would like to thank Jonathan Dushoff for thoughtful comments.
This study was funded by NSERC Discovery Grant.
